---
output:
  html_document: default
  pdf_document: default
  word_document: default
---

#Markdown for PhylotaR

This is a way to make structured and reproducable documentation of all steps that are taken in the Asteraceae supermatrix.

```{r cache=TRUE}
load("Environment_2.RData")
```

##Installing PhylotaR

The first step in the pipeline is downloading PhylotaR. Make sure that the latest version of R is installed on your pc. 

```{r eval=FALSE}
install.packages("devtools")
install.packages("remotes")
library(devtools)
library(remotes)
remotes::install_github('ropensci/phylotaR')
library(phylotaR)
```

##Seting up PhylotaR

Now we can start by setting up a working directory that contains certain parameters that are important for the analysis.

```{r eval=FALSE}
library(phylotaR)
wd <- '[FILEPATH TO WORKING DIRECTORY]'
ncbi_dr <- '[FILEPATH TO COMPILED BLAST+ TOOLS]'
txid <- 4210  # Asteracea ID
setup(wd = wd, txid = txid, ncbi_dr = ncbi_dr)
```

The Filepaths are of course different for each pc. In this case I have used the taxonomic ID of Asteraceae. But this can be altered. Use the taxonomic ID that is specified at [GenBank Taxonomy Browser](https://www.ncbi.nlm.nih.gov/Taxonomy/Browser/wwwtax.cgi?mode=Root)

Running PhylotaR is as simple as typing:

```{r eval=FALSE}

run(wd=wd)
```

##Interacting with the PhylotaR-object

After this has run, whenever you are in the same working directory you can call the PhylotaR-object again by running:


```{r eval=FALSE}
phylota=read_phylota(wd)
```

This object is easy to handle in R. The steps I took to create files per cluster are the following:


* **Create a new Phylota-object that has one sequence per taxon.**

```{r eval=FALSE}
phylota_sp <- drop_by_rank(phylota = phylota, rnk = 'species', n = 1)

```


* **Create a object (list) of cluster IDs. This is necessary to handle the object.**

```{r eval=FALSE}
cids=phylota_sp@cids
```

* **Create a new Phylota-object, but with excluding clusters that only contain a few taxa. Cut-off is flexible. A summary is a nice way to look what object you're left with.**

```{r eval=FALSE}
ntaxa=get_ntaxa(phylota = phylota_sp, cid = cids)#number of taxa per cluster
keep=cids[ntaxa>50]#new set of cluster IDs with more than 50 taxa
selected=drop_clstrs(phylota = phylota_sp, cid = keep)#new Phylota-object
```
```{r echo=FALSE}
head(smmry_sel)
```
  



##The loop that creates the final files per cluster.

I download a program that makes handling strings easier, which is important for the output filename.

```{r eval=FALSE}
install.packages("tidyverse")
library(tidyverse)
```

Then a new list of cluster IDs in this object is necessary.

```{r eval=FALSE}
cids_sel=selected@cids
```

And now the loop.

```{r eval=FALSE}
#A for loop that goes over the cluster IDs
for (i in cids_sel){
  txids <- get_txids(phylota = selected, cid = i, rnk = 'species')#makes a list of taxon-IDs for the specific cluster
  
# look up name for Taxon IDs per cluster and create a list out of it.
scientific_names <- get_tx_slot(phylota = selected, txid = txids, slt_nm = 'scnm')

#formatting the names
scientific_names <- gsub('\\.', '', scientific_names)
scientific_names <- gsub('\\s+', '_', scientific_names)

#specify the sequence IDs per cluster
  sids <- reduced@clstrs[[i]]@sids
  
  # write out (one file per cluster)
  pad="C:/Users/Bart/Documents/MBI jaar 3/Stage/Data/Results/cluster"#general path to location
  outfile= str_c(pad, i)#add the cluster ID to the filename
  write_sqs(phylota = selected, sid = sids, sq_nm = scientific_names,
            outfile = outfile)}
```

Now you have your files. Good luck!


##New section: Creating a species list of the entire object.

```{r eval=FALSE}
txids=selected@txids #Extract all taxon IDs

scientific_names <- get_tx_slot(phylota = selected, txid = txids, slt_nm = 'scnm') #Change IDs into scientific names

scientific_names=as.data.frame(scientific_names) #Make it a dataframe

write.csv(scientific_names, "C:/Users/Bart/Documents/MBI jaar 3/Stage/Data/phylotar-asteraceae/taxa.csv", row.names = T) #Write a csv-file from the dataframe.
```
 Now you also have a species list for further operartions. 